\vfill World of Warcraft's New Way to Get You Hooked

### 2013-04-03 paper.tex
3. Added in actual amount of money Blizz makes every month. With citation.

\subsubsection{Interests of Blizzard Entertainment}
Blizzard Entertainment is a publicly traded company. \cite{BlizzStock} As such its main goal is to show its shareholders that it is profiting and increasing the volume of business it handles. In no uncertain terms, Blizzard Entertainment wants as many people to buy and play their games, World of Warcraft included, as possible. Since World of Warcraft is subscription-based \cite{WoWSubscription}, Blizzard Entertainment earns money every single month from World of Warcraft players. None of the other games that Blizzard makes are subscription based. \cite{BlizzGameList} That means that Blizzard only ever receives one payment for any of its other games from customers. Blizzard Entertainment's interests are in getting more players to buy their games, particularly World of Warcraft which nets them money every month in addition to the initial cost.

>>>>

\subsubsection{Interests of Blizzard Entertainment}
Blizzard Entertainment is a publicly traded company. \cite{BlizzStock} As such its main goal is to show its shareholders that it is profiting and increasing the volume of business it handles. In no uncertain terms, Blizzard Entertainment wants as many people to buy and play their games, World of Warcraft included, as possible. Since World of Warcraft is subscription-based \cite{WoWSubscription}, Blizzard Entertainment earns money every single month from World of Warcraft players. None of the other games that Blizzard makes are subscription based. \cite{BlizzGameList} That means that Blizzard only ever receives one payment for any of its other games from customers. Blizzard Entertainment's interests are in getting more players to buy their games, particularly World of Warcraft which nets them \$13-15 every month in addition to the initial cost. \cite{WoWSubPlans}
